---
title: "Degree Priors"
author: "Owen Ward"
date: '`r Sys.Date()`'
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: FALSE
    code_folding: hide
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

data_path <- "../output/"

func_dir <- "../lib/"

library(rstan)
Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
options(mc.cores = parallel::detectCores())
library(tidyverse)
library(R.utils)
library(fields)
library(bayesplot)
library(compete)
library(RColorBrewer)
source(paste(func_dir,'naiveRankHierarchy.R',sep = ""))
source(paste(func_dir,'expertRankHierarchy.R',sep = ""))
source(paste(func_dir,'cleanData.R',sep = "")) 
source(paste(func_dir,'prepareDataStan.R',sep = "")) 
source(paste(func_dir,'inferLatentMmhp.R',sep = ""))
source(paste(func_dir,'plotUtil.R',sep = "")) 
source(paste(func_dir,'mmhp.R',sep = ""))
source(paste(func_dir,'uniHawkes.R',sep = ""))
source(paste(func_dir,'simulatePrediction.R',sep = ""))
source(paste(func_dir,'myGlicko.R',sep = ""))
source(paste(func_dir,'matrixPlotParameter.R',sep = ""))
source(paste(func_dir,'residualStructureScore.R',sep = ""))
source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")


source("C:/Users/owenw/Dropbox/with Owen/code/part3/lib/intensityPlot.R")
source("C:/Users/owenw/Dropbox/with Owen/code/part3/lib/uniHawkes.R")

theme_set(theme_minimal())

model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})


```


```{r mice_setup,include=FALSE,echo=FALSE, cache=TRUE}
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
cut_off <- 3
mice_number <- 12

full_data <- readRDS("../data/mice.RData")
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
cut_off <- 3
mice_number <- 12

# Define the cohorts will be fitted
fit_cohorts <- c(1:10)
naive_rank_10 <- list()
expert_rank_10 <- list()
for(current_cohort in fit_cohorts){
  naive_rank_10[[current_cohort]] <- naiveRankHierarchy(full_data[[cohort_names[current_cohort]]])
  expert_rank_10[[current_cohort]] <- expertRankHierarchy(full_data[[cohort_names[current_cohort]]])
}


```



While the currently implemented degree corrected C-MMHP model gives
good overall results, the `double_exponential` priors used for the degree 
rate parameters `gamma` and `zeta` lead to issues with mixing of these
chains. As such, we wish to identify a better choice of prior here
and see how this effects the downstream tasks performed.


# Run for longer

The simplest solution to these mixing issues is to fit the same model,
but adapting some of the stan fit parameters to avoid issues with sampling.

In particular, we consider

- `adapt_delta = 0.999`
- `max_treedepth = 15`

These makes this fit even more computationally demanding. Only several
cohorts were able to complete, for which the overall results looked similar.

Diagnostic plots will be included.

```{r}
orig_data_path <- "../output/"


lognor_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_lognor/"

long_run_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_tree_depth/"


current_cohort <- 8

# compare long run first


# load original fit 

load(paste(orig_data_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
old_fit <- fit_cohort_mmhp
bayesplot::rhat(old_fit)


load(paste(long_run_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
long_fit <- fit_cohort_mmhp
bayesplot::rhat(long_fit)
```



```{r}
m3_pr_orig <- readRDS(paste(orig_data_path,cohort_names[current_cohort],
                       "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

m3_pr_long <- readRDS(paste(long_run_path,cohort_names[current_cohort],
                       "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

summary(as.vector(m3_pr_long-m3_pr_orig))

#####
m1_pr <- readRDS(paste(orig_data_path,cohort_names[current_cohort],
                       "/chp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

m2_pr <- readRDS(paste(orig_data_path,cohort_names[current_cohort],
                       "/dchp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

# m3_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
#                        "/cmmhp_pr_matrix_",cohort_names[current_cohort],
#                        ".RDS",sep=''))

indep_pr <- readRDS(paste(orig_data_path,cohort_names[current_cohort],
                          "/immhp_pr_matrix_",cohort_names[current_cohort],
                          ".RDS",sep=''))

matrix_lst_plot <- list(
  indep_pr[rev(expert_rank_10[[current_cohort]]),
           expert_rank_10[[current_cohort]]],
  m1_pr[rev(expert_rank_10[[current_cohort]]),
        expert_rank_10[[current_cohort]]],
  m2_pr[rev(expert_rank_10[[current_cohort]]),
        expert_rank_10[[current_cohort]]],
  m3_pr_orig[rev(expert_rank_10[[current_cohort]]),
        expert_rank_10[[current_cohort]]]) 
cat("Cohort ",current_cohort,"\n",sep="")
myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                  xLabels=expert_rank_10[[current_cohort]],
                  yLabels=rev(expert_rank_10[[current_cohort]]),
                  min=-60,max=60,axis_cex=2,title_cex = 1.8,
                  colorPalette="RdBu",if.emp=FALSE,
                  #legend.mar=c(0.5,.5,0.5,0.5),
                  title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
                  #title_lst = list("I-MMHP"),
                  col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
                  matrix.mar=c(2.5,2.5,2.5,1)
)

matrix_lst_plot <- list(
  indep_pr[rev(expert_rank_10[[current_cohort]]),
           expert_rank_10[[current_cohort]]],
  m1_pr[rev(expert_rank_10[[current_cohort]]),
        expert_rank_10[[current_cohort]]],
  m2_pr[rev(expert_rank_10[[current_cohort]]),
        expert_rank_10[[current_cohort]]],
  m3_pr_long[rev(expert_rank_10[[current_cohort]]),
        expert_rank_10[[current_cohort]]]) 
cat("Cohort ",current_cohort,"\n",sep="")
myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                  xLabels=expert_rank_10[[current_cohort]],
                  yLabels=rev(expert_rank_10[[current_cohort]]),
                  min=-60,max=60,axis_cex=2,title_cex = 1.8,
                  colorPalette="RdBu",if.emp=FALSE,
                  #legend.mar=c(0.5,.5,0.5,0.5),
                  title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
                  #title_lst = list("I-MMHP"),
                  col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
                  matrix.mar=c(2.5,2.5,2.5,1)
)

```


# Lognormal priors

Alternatively, we consider lognormal priors for `gamma` and `zeta`. We
consider `model_3_1_bound.stan`, with `gamma ~ lognormal(0,1)` and
`zeta ~ lognormal(0,1)` also.



```{r}
lgnor_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_lnor/"

```



```{r compare a cohort}
current_cohort <- 3

load(paste(data_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

orig_fit <- fit_cohort_mmhp
orig_sim <- sim_cohort_mmhp


load(paste(lgnor_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

lnor_fit <- fit_cohort_mmhp
lnor_sim <- sim_cohort_mmhp

```




```{r}
rstan::check_hmc_diagnostics(orig_fit)
rstan::check_hmc_diagnostics(lnor_fit)
```

```{r}
summary(bayesplot::rhat(orig_fit))
summary(bayesplot::rhat(lnor_fit))

```

```{r}
apply(orig_sim$f,2,mean) - apply(lnor_sim$f,2,mean)


plot(apply(orig_sim$f,2,mean),apply(lnor_sim$f,2,mean))

plot(apply(orig_sim$lambda0,2,mean),apply(lnor_sim$lambda0,2,mean))

plot(apply(orig_sim$gamma,2,mean),apply(lnor_sim$gamma,2,mean))
plot(apply(orig_sim$zeta,2,mean),apply(lnor_sim$zeta,2,mean))


hist(apply(orig_sim$lambda0,2,mean) - apply(lnor_sim$lambda0,2,mean))

```

```{r}
mean(orig_sim$w_lambda)-mean(lnor_sim$w_lambda)
mean(lnor_sim$w_lambda)
```

This indicates.

```{r}
plot(orig_sim$w_lambda,lnor_sim$w_lambda)
#dim(orig_sim$alpha)

plot(orig_sim$alpha,lnor_sim$alpha)

plot(orig_sim$beta,lnor_sim$beta)

```



```{r pr-matrices}

for(current_cohort in 1:10) {
  m3_pr_orig <- readRDS(paste(data_path,cohort_names[current_cohort],
                       "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

  m3_pr_lnor <- readRDS(paste(lgnor_path,cohort_names[current_cohort],
                         "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                         ".RDS",sep=''))
  
  summary(as.vector(m3_pr_lnor-m3_pr_orig))
  
  #####
  m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                         "/chp_pr_matrix_",cohort_names[current_cohort],
                         ".RDS",sep=''))
  
  m2_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                         "/dchp_pr_matrix_",cohort_names[current_cohort],
                         ".RDS",sep=''))
  
  # m3_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
  #                        "/cmmhp_pr_matrix_",cohort_names[current_cohort],
  #                        ".RDS",sep=''))
  
  indep_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                            "/immhp_pr_matrix_",cohort_names[current_cohort],
                            ".RDS",sep=''))
  
  cat("Cohort ",current_cohort,"\n",sep="")
  
  matrix_lst_plot <- list(
    indep_pr[rev(expert_rank_10[[current_cohort]]),
             expert_rank_10[[current_cohort]]],
    m1_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m2_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m3_pr_orig[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]]) 
  #cat("Cohort ",current_cohort,"\n",sep="")
  myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]),
                    min=-60,max=60,axis_cex=2,title_cex = 1.8,
                    colorPalette="RdBu",if.emp=FALSE,
                    #legend.mar=c(0.5,.5,0.5,0.5),
                    title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
                    #title_lst = list("I-MMHP"),
                    col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
                    matrix.mar=c(2.5,2.5,2.5,1)
  )
  
  matrix_lst_plot <- list(
    indep_pr[rev(expert_rank_10[[current_cohort]]),
             expert_rank_10[[current_cohort]]],
    m1_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m2_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m3_pr_lnor[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]]) 
  #cat("Cohort ",current_cohort,"\n",sep="")
  myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]),
                    min=-60,max=60,axis_cex=2,title_cex = 1.8,
                    colorPalette="RdBu",if.emp=FALSE,
                    #legend.mar=c(0.5,.5,0.5,0.5),
                    title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
                    #title_lst = list("I-MMHP"),
                    col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
                    matrix.mar=c(2.5,2.5,2.5,1)
  )
}



```

# Exponential Priors


```{r}
exp_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_exp/"


```

```{r}
current_cohort <- 7

load(paste(data_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

orig_fit <- fit_cohort_mmhp
orig_sim <- sim_cohort_mmhp


load(paste(exp_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

exp_fit <- fit_cohort_mmhp
exp_sim <- sim_cohort_mmhp
```


```{r}
summary(bayesplot::rhat(orig_fit)[-588])
summary(bayesplot::rhat(exp_fit)[-588])
```
Cohorts 7 and 10 still look bad although an improvement for 9.

```{r}
apply(orig_sim$f,2,mean) - apply(exp_sim$f,2,mean)


plot(apply(orig_sim$f,2,mean),apply(exp_sim$f,2,mean))

plot(apply(orig_sim$lambda0,2,mean),apply(exp_sim$lambda0,2,mean))

plot(apply(orig_sim$gamma,2,mean),apply(exp_sim$gamma,2,mean))
plot(apply(orig_sim$zeta,2,mean),apply(exp_sim$zeta,2,mean))


hist(apply(orig_sim$lambda0,2,mean) - apply(exp_sim$lambda0,2,mean))
```



```{r}
fit_cohorts <- 1:10
fit_cohorts <- fit_cohorts[c(-1,-3,-5,-6)]

for(current_cohort in fit_cohorts) {
  m3_pr_orig <- readRDS(paste(data_path,cohort_names[current_cohort],
                       "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

  m3_pr_exp <- readRDS(paste(exp_path,cohort_names[current_cohort],
                         "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                         ".RDS",sep=''))
  
  summary(as.vector(m3_pr_exp-m3_pr_orig))
  
  #####
  m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                         "/chp_pr_matrix_",cohort_names[current_cohort],
                         ".RDS",sep=''))
  
  m2_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                         "/dchp_pr_matrix_",cohort_names[current_cohort],
                         ".RDS",sep=''))
  
  # m3_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
  #                        "/cmmhp_pr_matrix_",cohort_names[current_cohort],
  #                        ".RDS",sep=''))
  
  indep_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                            "/immhp_pr_matrix_",cohort_names[current_cohort],
                            ".RDS",sep=''))
  
  cat("Cohort ",current_cohort,"\n",sep="")
  
  matrix_lst_plot <- list(
    indep_pr[rev(expert_rank_10[[current_cohort]]),
             expert_rank_10[[current_cohort]]],
    m1_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m2_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m3_pr_orig[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]]) 
  #cat("Cohort ",current_cohort,"\n",sep="")
  myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]),
                    min=-60,max=60,axis_cex=2,title_cex = 1.8,
                    colorPalette="RdBu",if.emp=FALSE,
                    #legend.mar=c(0.5,.5,0.5,0.5),
                    title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
                    #title_lst = list("I-MMHP"),
                    col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
                    matrix.mar=c(2.5,2.5,2.5,1)
  )
  
  matrix_lst_plot <- list(
    indep_pr[rev(expert_rank_10[[current_cohort]]),
             expert_rank_10[[current_cohort]]],
    m1_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m2_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m3_pr_lnor[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]]) 
  #cat("Cohort ",current_cohort,"\n",sep="")
  myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]),
                    min=-60,max=60,axis_cex=2,title_cex = 1.8,
                    colorPalette="RdBu",if.emp=FALSE,
                    #legend.mar=c(0.5,.5,0.5,0.5),
                    title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
                    #title_lst = list("I-MMHP"),
                    col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
                    matrix.mar=c(2.5,2.5,2.5,1)
  )
}

```

# Inverse Gamma Prior

We instead consider `inv_gamma(1,0.5)` priors for both `gamma` and `zeta`.


```{r}
ing_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_invg_2/"

```



```{r compare a cohort inv gamma}
current_cohort <- 5

load(paste(data_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

orig_fit <- fit_cohort_mmhp
orig_sim <- sim_cohort_mmhp


load(paste(ing_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

ing_fit <- fit_cohort_mmhp
ing_sim <- sim_cohort_mmhp

```




```{r}
rstan::check_hmc_diagnostics(orig_fit)
rstan::check_hmc_diagnostics(ing_fit)
```

```{r}
summary(bayesplot::rhat(orig_fit))
summary(bayesplot::rhat(ing_fit))
```

```{r}
fit_cohorts <- 1:10
#fit_cohorts <- fit_cohorts[c(-1,-3,-5,-6)]


i_mmhp_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_folders/output_immhp/"

for(current_cohort in fit_cohorts) {
  m3_pr_orig <- readRDS(paste(data_path,cohort_names[current_cohort],
                       "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))

  m3_pr_ing <- readRDS(paste(ing_path,cohort_names[current_cohort],
                         "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                         ".RDS",sep=''))
  
  summary(as.vector(m3_pr_exp-m3_pr_orig))
  
  #####
  m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                         "/chp_pr_matrix_",cohort_names[current_cohort],
                         ".RDS",sep=''))
  
  m2_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                         "/dchp_pr_matrix_",cohort_names[current_cohort],
                         ".RDS",sep=''))
  
  # m3_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
  #                        "/cmmhp_pr_matrix_",cohort_names[current_cohort],
  #                        ".RDS",sep=''))
  
  indep_pr <- readRDS(paste(i_mmhp_path,cohort_names[current_cohort],
                            "/immhp_pr_matrix_",cohort_names[current_cohort],
                            ".RDS",sep=''))
  
  cat("Cohort ",current_cohort,"\n",sep="")
  
  matrix_lst_plot <- list(
    indep_pr[rev(expert_rank_10[[current_cohort]]),
             expert_rank_10[[current_cohort]]],
    m1_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m2_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m3_pr_orig[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]]) 
  #cat("Cohort ",current_cohort,"\n",sep="")
  myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]),
                    min=-60,max=60,axis_cex=2,title_cex = 1.8,
                    colorPalette="RdBu",if.emp=FALSE,
                    #legend.mar=c(0.5,.5,0.5,0.5),
                    title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
                    #title_lst = list("I-MMHP"),
                    col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
                    matrix.mar=c(2.5,2.5,2.5,1)
  )
  
  matrix_lst_plot <- list(
    indep_pr[rev(expert_rank_10[[current_cohort]]),
             expert_rank_10[[current_cohort]]],
    m1_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m2_pr[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]],
    m3_pr_lnor[rev(expert_rank_10[[current_cohort]]),
          expert_rank_10[[current_cohort]]]) 
  #cat("Cohort ",current_cohort,"\n",sep="")
  myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]),
                    min=-60,max=60,axis_cex=2,title_cex = 1.8,
                    colorPalette="RdBu",if.emp=FALSE,
                    #legend.mar=c(0.5,.5,0.5,0.5),
                    title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
                    #title_lst = list("I-MMHP"),
                    col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
                    matrix.mar=c(2.5,2.5,2.5,1)
  )
}

```

