---
title: "Priors for Latent Hawkes"
author: "Owen G. Ward"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
---

This notebook is to explore prior specifications on the estimated latent fit.

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/", echo = FALSE, include = FALSE,
                     message=FALSE)
# setting these to false to only show updates
knitr::opts_chunk$set(message = FALSE)

```


First load in required packages and set some useful paths. 
I shouldn't be writing to anything here.

```{r, include=FALSE}

# don't write to this path
orig_data_path <- "C:/Users/owenw/Google Drive/Tian/Research+JingWu/thesis_data/part2/real_data/"

new_data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/debug_orig_code/"

func_dir <- "C:/Users/owenw/Dropbox/with Owen/code/part2/lib/"


library(rstan)
Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
options(mc.cores = parallel::detectCores())
library(tidyverse)
library(R.utils)
library(fields)
library(bayesplot)
library(compete)
source(paste(func_dir,'naiveRankHierarchy.R',sep = ""))
source(paste(func_dir,'expertRankHierarchy.R',sep = ""))
source(paste(func_dir,'cleanData.R',sep = "")) 
source(paste(func_dir,'prepareDataStan.R',sep = "")) 
source(paste(func_dir,'inferLatentMmhp.R',sep = ""))
source(paste(func_dir,'plotUtil.R',sep = "")) 
source(paste(func_dir,'mmhp.R',sep = ""))
source(paste(func_dir,'uniHawkes.R',sep = ""))
source(paste(func_dir,'simulatePrediction.R',sep = ""))
source(paste(func_dir,'myGlicko.R',sep = ""))
source(paste(func_dir,'matrixPlotParameter.R',sep = ""))
source(paste(func_dir,'residualStructureScore.R',sep = ""))
source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")


theme_set(theme_minimal())

```



Then we want to compare the two fits, particularly for the cohorts
which differed.


```{r,echo=FALSE}
full_data <- readRDS("C:/Users/owenw/Dropbox/with Owen/code/part2/data/mice.RData")
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
cut_off <- 3
mice_number <- 12

# Define the cohorts will be fitted
fit_cohorts <- c(1:10)
naive_rank_10 <- list()
expert_rank_10 <- list()
out <- captureOutput(for(current_cohort in fit_cohorts){
  naive_rank_10[[current_cohort]] <- naiveRankHierarchy(full_data[[cohort_names[current_cohort]]])
  expert_rank_10[[current_cohort]] <- expertRankHierarchy(full_data[[cohort_names[current_cohort]]])
})


```


# Prior specification for the intensity parameters of MMHP

One concern is the choice of priors for $\lambda_0$ and $\lambda_1$, which is defined as
$\lambda_1 = w_{\lambda}\lambda_0$ for some $w_{\lambda} > 1$. The
priors are currently:

```{r, eval=FALSE}
  //priors
  lambda0 ~ lognormal(0,1);
  w_lambda ~ normal(0,2);  //lognormal
  eta_1 ~ lognormal(0,1);
  eta_2 ~ lognormal(0,1);
  eta_3 ~ lognormal(0,1);
  beta ~ normal(0,10);
  f[alpha_id] ~ normal(1,0.05);
  
```


We would like to consider better priors here. A more natural choice
of the priors would be `gamma` .

Perhaps most importantly is the results of the prior on the eventual latent
rankings.


## Prior 1

Here we consider

- `lambda0 ~ gamma(0.5,0.001)`
- `w_lambda ~ lognormal(0,2)`


We can examine the results of this and compare to the modified fits
for the first cohort.


```{r}
current_cohort <- 1 # testing on this cohort for now

priors_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/Prior_results/prior_1/"

refit_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/debug_copy/"

prior_fit <- readRDS(paste(priors_path,cohort_names[current_cohort],
                         "/cohort_mmhp_stan_fit_",
                         cohort_names[current_cohort],
                         ".RDS",sep = ''))

prior_sim1 <- readRDS(paste(priors_path,cohort_names[current_cohort],
                         "/cohort_mmhp_stan_draws_",
                         cohort_names[current_cohort],
                         ".RDS",sep = ''))

fit_cohort_mmhp_re <- readRDS(paste(refit_path,cohort_names[current_cohort],
                         "/cohort_mmhp_stan_fit_",
                         cohort_names[current_cohort],
                         ".RDS",sep = ''))

sim_cohort_mmhp_re <- readRDS(paste(refit_path,cohort_names[current_cohort],
                         "/cohort_mmhp_stan_draws_",
                         cohort_names[current_cohort],
                         ".RDS",sep = ''))



# want to compare orig_data_path to the new results

# load Jing's example for this version
load(paste(orig_data_path,cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))

```


Then we can compare the traceplots of both of these.

```{r}

traceplot(fit_cohort_mmhp,pars=c("lambda0","eta_1","eta_2","eta_3","beta","lambda1"))+
  ggtitle("Ignoring null counts")

traceplot(fit_cohort_mmhp_re,pars=c("lambda0","eta_1","eta_2","eta_3","beta","lambda1"))+
  ggtitle("Original priors, including null counts")

traceplot(prior_fit,
          pars=c("lambda0","eta_1","eta_2","eta_3","beta","lambda1"))+
  ggtitle("Prior 1")


```

And the corresponding rankings.

```{r}
traceplot(fit_cohort_mmhp,
          pars=c("f[1]","f[2]","f[3]","f[4]","f[5]","f[6]",
                 "f[7]","f[8]","f[9]","f[10]","f[11]","f[12]"))+
  ggtitle("Ignoring null counts")

traceplot(fit_cohort_mmhp_re,
          pars=c("f[1]","f[2]","f[3]","f[4]","f[5]","f[6]",
                 "f[7]","f[8]","f[9]","f[10]","f[11]","f[12]"))+
  ggtitle("Original priors, including null counts")

traceplot(prior_fit,
          pars=c("f[1]","f[2]","f[3]","f[4]","f[5]","f[6]",
                 "f[7]","f[8]","f[9]","f[10]","f[11]","f[12]"))+
  ggtitle("Prior 1")
```


So this actually leads to even smaller values of `lambda0`, with similar
`lambda1`, but both are still quite different from excluding the null counts.


```{r}
orig_f <-apply(sim_cohort_mmhp$f,2,mean)
refit_f <- apply(sim_cohort_mmhp_re$f,2,mean)
p1_f <- apply(prior_sim1$f,2,mean)

tibble(orig_f,refit_f,p1_f) %>%
  ggplot(aes(orig_f,refit_f)) + geom_point()

tibble(orig_f,refit_f,p1_f) %>%
  ggplot(aes(orig_f,p1_f)) + geom_point()


```

Similarly, the Pearson residual matrices for each of these fits. I only have these
for the new priors and the refits, and I can load in what Jing has saved.






## Prior 2

As a test, lets repeat with a strong prior for `lambda0`

- `lambda0 ~ gamma(1000,1000)`
- `w_lambda ~ lognormal(0,2)`



```{r}
current_cohort <- 1 # testing on this cohort for now

priors_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/Prior_results/prior_2/"

refit_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/debug_copy/"

prior_fit <- readRDS(paste(priors_path,cohort_names[current_cohort],
                         "/cohort_mmhp_stan_fit_",
                         cohort_names[current_cohort],
                         ".RDS",sep = ''))

prior_sim2 <- readRDS(paste(priors_path,cohort_names[current_cohort],
                         "/cohort_mmhp_stan_draws_",
                         cohort_names[current_cohort],
                         ".RDS",sep = ''))

# fit_cohort_mmhp_re <- readRDS(paste(refit_path,cohort_names[current_cohort],
#                          "/cohort_mmhp_stan_fit_",
#                          cohort_names[current_cohort],
#                          ".RDS",sep = ''))
# 
# 
# # want to compare orig_data_path to the new results
# 
# # load Jing's example for this version
# load(paste(orig_data_path,cohort_names[current_cohort],
#              "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
#              ".RData",sep=''))

traceplot(fit_cohort_mmhp,pars=c("lambda0","eta_1","eta_2","eta_3","beta","lambda1"))+
  ggtitle("Ignoring null counts")

traceplot(fit_cohort_mmhp_re,pars=c("lambda0","eta_1","eta_2","eta_3","beta","lambda1"))+
  ggtitle("Original priors, including null counts")

traceplot(prior_fit,
          pars=c("lambda0","eta_1","eta_2","eta_3","beta","lambda1"))+
  ggtitle("Prior 2")

```

This doesn't work either, as it essentially seems to pull `lambda0` and
`lambda1` together.




For example, the results from prior 2 for the rankings.

```{r}
traceplot(fit_cohort_mmhp,
          pars=c("f[1]","f[2]","f[3]","f[4]","f[5]","f[6]",
                 "f[7]","f[8]","f[9]","f[10]","f[11]","f[12]"))+
  ggtitle("Original priors, ignoring null counts")

traceplot(fit_cohort_mmhp_re,
          pars=c("f[1]","f[2]","f[3]","f[4]","f[5]","f[6]",
                 "f[7]","f[8]","f[9]","f[10]","f[11]","f[12]"))+
  ggtitle("Original priors, including null counts")

traceplot(prior_fit,
          pars=c("f[1]","f[2]","f[3]","f[4]","f[5]","f[6]",
                 "f[7]","f[8]","f[9]","f[10]","f[11]","f[12]"))+
  ggtitle("Prior 2")
```

```{r}
p2_f <- apply(prior_sim2$f,2,mean)

tibble(orig_f,refit_f,p2_f) %>%
  ggplot(aes(orig_f,refit_f)) + geom_point()

tibble(orig_f,refit_f,p1_f) %>%
  ggplot(aes(orig_f,p2_f)) + geom_point()
```




## Other priors? 

- What other priors could be considered here?
- Have not considered changing the priors for the `eta` parameters.




```{r plot_setup,include=FALSE}
data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/debug_copy/"
jing_data_path <- "C:/Users/owenw/Google Drive/Tian/Research+JingWu/thesis_data/part2/real_data/"
plot_path = "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/plots/"

```


# Construct Pearson residuals from these fits

```{r}
# load Jing's PR_matrices

load("C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/pearson_residual_original.RData")

orig_pr <- m3_residual_matrix_lst[[1]]

# load in prior PR_matrices
priors_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/Prior_results/prior_1/"
prior1_pr <- readRDS(paste(priors_path,cohort_names[current_cohort],
                         "/cmmhp_pr_matrix_",
                         cohort_names[current_cohort],
                         ".RDS",sep = ''))

priors_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/Prior_results/prior_2/"
prior2_pr <- readRDS(paste(priors_path,cohort_names[current_cohort],
                         "/cmmhp_pr_matrix_",
                         cohort_names[current_cohort],
                         ".RDS",sep = ''))

# for orig fit, I have a copy of this somewhere also, maybe not locally

# orig_pr
# prior1_pr
```


```{r, include=FALSE}
matrix_lst_plot <- list(
                        orig_pr[rev(expert_rank_10[[current_cohort]]),
                                                  expert_rank_10[[current_cohort]]],
                        prior1_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        prior2_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]]
                        
                        )

myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=3,n_row=3,
                  xLabels=expert_rank_10[[current_cohort]],
                  yLabels=rev(expert_rank_10[[current_cohort]]),
                  min=-63,max=63,axis_cex=2,title_cex = 1.8,
                  colorPalette="RdBu",if.emp=FALSE,legend.mar=c(0.5,.5,0.5,0.05),
                  title_lst=list("Orig","Prior 1","Prior 2"), 
                  #title_lst = list("I-MMHP"),
                  col_axis=c(-60,-30,0,30,60), 
                  out.title="", fake_matrix=FALSE,
                  matrix.mar=c(1.5,1.5,1.5,1))

```


```{r,fig.width=6}
library(plot.matrix)
plot(orig_pr[rev(expert_rank_10[[current_cohort]]),
                                                  expert_rank_10[[current_cohort]]],
     main = "Original")
plot(prior1_pr[rev(expert_rank_10[[current_cohort]]),
                                                  expert_rank_10[[current_cohort]]],
     main = "Prior 1")

plot(prior2_pr[rev(expert_rank_10[[current_cohort]]),
                                                  expert_rank_10[[current_cohort]]],
     main = "Prior 2")



```


So although these priors appear to give similar results in terms of latent
rankings, the estimated MMHP parameters differ widely, leading 
to very different measures of fit.


- What about other outputs?


# Rank comparisons 


```{r}

orig_f <- sim_cohort_mmhp$f

colnames(orig_f) <- paste("f_",c(1:12),sep = "")

orig_f <- as_tibble(orig_f) %>% 
  mutate(sim = row_number()) %>%
 pivot_longer(cols = starts_with("f")) 
orig_f %>%
  ggplot(aes(name,value)) + geom_boxplot() +
  ggtitle("Original Fit, no empty windows")

refit_f <- sim_cohort_mmhp_re$f

colnames(refit_f) <- paste("f_",c(1:12),sep = "")

refit_f <-as_tibble(refit_f) %>% 
  mutate(sim = row_number()) %>%
 pivot_longer(cols = starts_with("f")) 
refit_f %>%
  ggplot(aes(name,value)) + geom_boxplot() +
  ggtitle("Original Fit, with empty windows")

 
p1_f <- prior_sim1$f

colnames(p1_f) <- paste("f_",c(1:12),sep = "")

p1_f <-as_tibble(p1_f) %>% 
  mutate(sim = row_number()) %>%
 pivot_longer(cols = starts_with("f")) 
p1_f %>%
  ggplot(aes(name,value)) + geom_boxplot() +
  ggtitle("Prior 1")


p2_f <- prior_sim2$f

colnames(p2_f) <- paste("f_",c(1:12),sep = "")

p2_f <- as_tibble(p2_f) %>% 
  mutate(sim = row_number()) %>%
 pivot_longer(cols = starts_with("f")) 
p2_f %>%
  ggplot(aes(name,value)) + geom_boxplot() +
  ggtitle("Prior 2")


```

Plot these all in  the one plot.

```{r}
orig_f$model <- "orig"
refit_f$model <- "refit"
p1_f$model <- "p1"
p2_f$model <- "p2"


bind_rows(orig_f,refit_f,p1_f,p2_f) %>%
  ggplot(aes(name,value)) + 
  geom_boxplot(aes(colour = model))
  

```

So the latent rankings are somewhat similar, even if these lead to
vastly different Pearson residuals.
